---
title: 'Problem Set 0: Bias in Self-reported Turnout'
author: "Shuai"
date: '2022-05-14'
output:
  pdf_document: default
  html_document: default
---

```{r}
turnout <- read.csv("turnout.csv")

t_dim <- dim(turnout)
year_range <- range(turnout$year)
```

Q1: How many observations are there? What is the range of years covered in this data set?

A1: There are `r length(names(turnout))` observations. The range of years covered in this data set is from `r min(turnout$year)` to `r max(turnout$year)`.

```{r}
turnout$VAPtr <- turnout$total / (turnout$VAP + turnout$overseas) * 100
turnout$VEPtr <- turnout$total / turnout$VEP * 100

knitr::kable(turnout[,c("year", "VAPtr", "VEPtr")])
```

Q2: What difference do you observe between the different measures of turnout?

A2: `r c(turnout$VEPtr - turnout$VAPtr)`

```{r}
turnout$diffVAP <- turnout$ANES - turnout$VAPtr
turnout$diffVEP <- turnout$ANES - turnout$VEPtr

turnout[,c("diffVAP", "diffVEP")]
```

Q3: How big are each of these differences on average? What is the range of the differences?

A3:

- average of diffVAP: `r mean(turnout$diffVAP)`, average of diffVEP: `r mean(turnout$diffVEP)`
- range of diffVAP: (`r range(turnout$diffVAP)`)
- range of diffVEP: (`r range(turnout$diffVEP)`)
